Supplement for: Carbon cycling in mature and regrowth forests globally

### 2021-01-25 manuscript/response_to_reviews.Rmd

**We prefer not to separate forests of known age into categories, but rather to represent age as a continuous variable, when possible. In large part this is motivated by the fact that appropriate age thresholds for various categories would vary across biomes, given differences in biomass accumulation rates. While our ideal would be to have no categorical divisions, unknown stand ages--particularly in the tropics--force us to divide the data into the categories used here.**

**To provide a better representation of age trends, we created new figure 9. Although it does not break forests into additional age categories, it does address what seems to be at the core of this concern, which is a concise representation of differences across the full range of stand ages.**

The consistency check (e.g. do component fluxes/pools sum to within one standard deviation of the aggregate flux or pool) seems like it is destined to provide a favorable assessment of the degree of closure so long as the data within each grouping represent a wide range of natural climatic and soil variability. As long as the aggregate variable has a large standard deviation, the results are likely guaranteed to be “consistent.” It seems this metric would benefit from some simulations (perhaps with artificially generated data) to understand exactly how poor closure needs to be at the site-level to generate an inconsistent results when aggregated across sites.

**We agree that such an analysis would be valuable, but time and resource constraints place it beyond the scope of what is currently feasible in this already very large analysis. We also note that the focus is now shifted towards the ecological questions (trends across biomes and with age), dropping as a main focus the original question on database representativeness and C cycle closure.**

**We believe that the current consistency check is valuable as a first pass for identifying cases of extreme mis-matches, and therefore retain it as is. However, we agree that it is not the ideal test, and that it is not very stringent (given high standard deviations) and have therefore toned down claims that the budgets are "closed"/"internally consistent" throughout the manuscript (e.g., removed from abstract). We note that the discussion already stated that our criteria for closure was relatively loose (and this statement is unchanged in the revised version): "On the other, however, *ForC* derives data from multiple heterogeneous sources, and standard deviations within each biome are high; as a result, the standard for C closure is relatively loose [*c.f.* @houghton_terrestrial_2020]."**

### 2021-01-25 manuscript/ERL_global_C_review.Rmd
proofreed through p. 16

Stand age is another important axis of variation in forest C cycling (Fig. `r schematic`).
In 1969, E.P. Odum's "The Strategy of Ecosystem Development" laid out predictions as to how forest energy flows and organic matter stocks vary with stand age  [@odum_strategy_1969].
Although the conceptualization of the C cycle in this paper was simplistic by current standards, the paper was foundational in framing the theory around which research on the subject still revolves [@corman_foundations_2019], and the basic framework still holds, albeit with modest modifications [Fig. `r schematic`; @andersonteixeira_altered_2013].
Following stand-clearing disturbance, $GPP$, $NPP$, and biomass of leaves ($B_{foliage}$) and fine roots ($B_{root-fine}$) increase rapidly and thereafter remain relatively stable ($B_{foliage}$, $B_{root-fine}$, sometimes $GPP$) or decline slightly [$NPP$, sometimes $GPP$; e.g., @law_changes_2003; @pregitzer_carbon_2004; @amiro_ecosystem_2010; @goulden_patterns_2011].
The decline in $NPP$ occurs because $R_{auto}$ increases relative to $GPP$ as forests age, corresponding to declining carbon use efficiency with stand age [@delucia_forest_2007; @collalti_forest_2020].
Heterotrophic respiration, most of which originates from the soil ($R_{het-soil}$) remains relatively constant with stand age [@law_changes_2003; @pregitzer_carbon_2004; @goulden_patterns_2011], with the result that net ecosystem production ($NEP=GPP-R_{eco}$, where $R_{eco}$ is total ecosystem respiration) is initially negative, increases to a maximum at intermediate ages, and declines thereafter [@law_changes_2003; @pregitzer_carbon_2004; @amiro_ecosystem_2010; @goulden_patterns_2011; @luyssaert_old-growth_2008].
The result is that biomass accumulates rapidly in young forests, followed by a slow decline to near zero in old forests [e.g., @lichstein_biomass_2009; @yang_carbon_2011].
While these trends have been subject of fairly recent qualitative review [@andersonteixeira_altered_2013], there is need for a synthetic, quantitative review taking advantage of the greatly expanded data now available.

@@

There were sufficient data to assess differences among biomes in mature forest values for 15 flux variables, and significant differences among biomes were detected for 12 variables (Table 1).
In all of these cases--including C fluxes into, within, and out of the ecosystem--C fluxes were highest in tropical forests, intermediate in temperate (broadleaf or conifer) forests, and lowest in boreal forests (Table 1, Figs. `r flux_age_trends`, `r all_flux_age_trends`).
Differences between tropical and boreal forests were always significant, with temperate forests intermediate and significantly different from one or both.
Fluxes tended to be numerically greater in temperate broadleaf than temperate conifer forests, but the difference was never statistically significant.
This pattern held for the following variables: $GPP$, $NPP$, $ANPP$, $ANPP_{stem}$,$ANPP_{branch}$, $ANPP_{foliage}$, $BNPP$, $R_{eco}$, $R_{root}$, $R_{soil}$, and $R_{het-soil}$. 
For two of the variables without significant differences among biomes ($ANPP_{litterfall}$ and $BNPP_{fine}$; Figs. `r ANPP_litterfall_fig` and `r BNPP_fine_fig`, respectively), the same general trends applied but were not statistically significant. 
Another exception was for $BNPP_{root-coarse}$, where all records came from high-biomass forests in the US Pacific Northwest, resulting in marginally higher values for the temperate conifer biome (Table 1, Fig. `r BNPP_coarse_fig`; differences significant in mixed effects model but not in post-hoc pairwise comparison).

The most notable exception to the pattern of decreasing flux per unit area from tropical to boreal biomes was $NEP$, with no significant differences across biomes but with the largest average in temperate broadleaf forests, followed by tropical, boreal, and temperate conifer forests (Figs. `r flux_age_trends`, `r NEP_fig`).

>>>>

Stand age is another important axis of variation in forest C cycling (Fig. `r schematic`).
In 1969, E.P. Odum's "The Strategy of Ecosystem Development" laid out predictions as to how forest energy flows and organic matter stocks vary with stand age  [@odum_strategy_1969].
Although the conceptualization of the C cycle in this paper was simplistic by current standards, the paper was foundational in framing the theory around which research on the subject still revolves [@corman_foundations_2019], and the basic framework still holds, albeit with modest modifications [Fig. `r schematic`; @andersonteixeira_altered_2013].
Following stand-clearing disturbance, $GPP$, $NPP$, and biomass of leaves ($B_{foliage}$) and fine roots ($B_{root-fine}$) increase rapidly and thereafter remain relatively stable ($B_{foliage}$, $B_{root-fine}$, sometimes $GPP$) or decline slightly [$NPP$, sometimes $GPP$; e.g., @law_changes_2003; @pregitzer_carbon_2004; @amiro_ecosystem_2010; @goulden_patterns_2011].
The decline in $NPP$ occurs because $R_{auto}$ increases relative to $GPP$ as forests age, corresponding to declining carbon use efficiency with stand age [@delucia_forest_2007; @collalti_forest_2020].
Heterotrophic respiration, most of which originates from the soil ($R_{het-soil}$) remains relatively constant with stand age [@law_changes_2003; @pregitzer_carbon_2004; @goulden_patterns_2011], with the result that net ecosystem production ($NEP=GPP-R_{eco}$, where $R_{eco}$ is total ecosystem respiration) is initially negative, increases to a maximum at intermediate ages, and declines--typically to a small positive value--thereafter [@law_changes_2003; @pregitzer_carbon_2004; @amiro_ecosystem_2010; @goulden_patterns_2011; @luyssaert_old-growth_2008].
The result is that biomass accumulates rapidly in young forests, followed by a slow decline to near zero in old forests [e.g., @lichstein_biomass_2009; @yang_carbon_2011].
While these trends have been subject of fairly recent qualitative review [@andersonteixeira_altered_2013], there is need for a synthetic, quantitative review taking advantage of the greatly expanded data now available.

@@

There were sufficient data to assess differences among biomes in mature forest values for 15 flux variables, and significant differences among biomes were detected for 12 variables (Table 1).
In all of these cases--including C fluxes into, within, and out of the ecosystem--C fluxes were highest in tropical forests, intermediate in temperate (broadleaf or conifer) forests, and lowest in boreal forests (Table 1, Figs. `r flux_age_trends`, `r all_flux_age_trends`).
Differences between tropical and boreal forests were always significant, with temperate forests intermediate and significantly different from one or both.
Fluxes tended to be numerically greater in temperate broadleaf than temperate conifer forests, but the difference was never statistically significant.
This pattern held for the following variables: $GPP$, $NPP$, $ANPP$, $ANPP_{stem}$,$ANPP_{branch}$, $ANPP_{foliage}$, $BNPP$, $R_{eco}$, $R_{root}$, $R_{soil}$, and $R_{het-soil}$. 
For two of the variables without significant differences among biomes ($ANPP_{litterfall}$ and $BNPP_{fine}$; Figs. `r ANPP_litterfall_fig` and `r BNPP_fine_fig`, respectively), the same general trends applied but were not statistically significant. 
Another exception was for $BNPP_{root-coarse}$, where all records came from high-biomass forests in the US Pacific Northwest, resulting in marginally higher values for the temperate conifer biome (Fig. `r BNPP_coarse_fig`; differences significant in mixed effects model but not in post-hoc pairwise comparison).

The most notable exception to the pattern of decreasing flux per unit area from tropical to boreal biomes was $NEP$, with no significant differences across biomes but with the largest average in temperate broadleaf forests, followed by tropical, boreal, and temperate conifer forests (Figs. `r flux_age_trends`, `r NEP_fig`).
For all biomes, $NEP$ was positive, with 95% confidence intervals excluding zero.
